Molecular dynamics simulation of synchronization in driven particles

### 2020-12-18 manuscript/manuscript_ajp_2020.tex
finished general introduction!

\section{Introduction} %
%
%Outline
%------------------------------------------------------------------
%synchronization = widest audience possible
Synchronization is a universal phenomena
where individual oscillators adjust rhythm due
to an external stimuli \cite{Pikovsky2003}.
%Christiaan Huygens 
%[has been adapted into many useful technologies...]
Huygens' 1665 experiments on
the 
motions of two pendula on wall-mounted clocks,
demonstrated the tendency of 
two periodic oscillators in close
proximity to swing in time, i.e. to synchronize \cite{Bennett2002}.
Physical synchronous behavior are observed
in many everyday systems
such as the
coupled flickering candle flames \cite{Okamoto2016} 
and metronomes \cite{Jia2015}.
Biological systems benefit from cooperative
synchronzation.
Birds coordinate
flapping of wings in order to optimize energy use during flight \cite{Portugal2014},
frogs communicate by croaking patterns dictated by location \cite{Aihara2014},
and humans synchronize clapping in time with music \cite{Tranchant2016}.

to simultaneous firing of neurons in cardiac muscle \cite{}
and brain tissue (i.e. brain waves) \cite{}.

Such systems can be driven to form new synchronized patterns,
for instance
firefly [swarms] signal in time with a pulsed light emitting diode \cite{},
[more examples]
Driven coupled oscillations are sufficiently
broad and useful to be the subject of computational modeling.

%phase locking

Synchronization can be modeled with numerical studies of confined 
driven particles.
Studies modeling synchronized behaviors
can be performed with
coupled oscillators []
An alternative method is to
study the dynamics of a single particle
confined in a periodic 
potential landscape subject
to with an applied driving force with constant or direct (DC)
and alterating (AC)
components.

@@

\bibitem{Pikovsky2003} A. Pikovsky, M. Rosenblum, and J. Kurths, {\it Synchronization: A Universal Concept in Nonlinear Sciences} (Cambridge Univ. Press, Cambridge, 2003).

@@

@@

>>>>

\section{Introduction} %
%
%Outline
%------------------------------------------------------------------
%synchronization = widest audience possible
Synchronization is a universal phenomena
where individual oscillators adjust rhythm due
to an external stimuli \cite{Pikovsky2003}.
%Christiaan Huygens 
%[has been adapted into many useful technologies...]
Huygens' 1665 experiments on
the 
motions of two pendula on wall-mounted clocks,
demonstrated the tendency of 
two periodic oscillators in close
proximity to swing in time, i.e. to synchronize \cite{Bennett2002}.
Physical synchronous behavior are observed
in many everyday systems
such as the
coupled flickering candle flames \cite{Okamoto2016} 
and metronomes \cite{Jia2015}.
Biological systems benefit from cooperative
synchronzation.
Birds coordinate
flapping of wings in order to optimize energy use during flight \cite{Portugal2014},
frogs communicate by croaking patterns dictated by location \cite{Aihara2014},
and humans synchronize clapping in time with music \cite{Tranchant2016}.
At a cellular level, 
neurons simultaneously fire in cardiac muscle \cite{MartinHall1999}
and brain tissue  \cite{Singer1999}.

%Given the prevalence of synchronization,
%it is the subject of many computational models.
Here we focus numerical studies 
of the synchronized dynamics
of confined particles driven over
a washboard shaped potential energy landscape. 
We chose this model for its
relevance to condensed matter systems

%phase locking
The hallmark of phase locking is
that the ratio of frequencies is an integer number \cite{Bak1986}

Studies modeling synchronized behaviors
can be performed with
coupled oscillators []
An alternative method is to
study the dynamics of a single particle
confined in a periodic 
potential landscape subject
to with an applied driving force with constant or direct (DC)
and alterating (AC)
components.

@@

  %intro to oscillators
\bibitem{Pikovsky2003} A. Pikovsky, M. Rosenblum, and J. Kurths, {\it Synchronization: A Universal Concept in Nonlinear Sciences} (Cambridge Univ. Press, Cambridge, 2003).

@@

  %biological examples

@@

  \bibitem{MartinHall1999} G. Martin Hall, Sonya Bahar, and Daniel J. Gauthier, Prevalence of Rate-Dependent Behaviors in Cardiac Muscle. Phys. Rev. Lett. {\bf 82}, 2995 (1999).

  \bibitem{Singer1999} W. Singer. Striving for coherence. Nature, {\bf 397} 391, 1999.

    %condensed matter intro
    \bibitem{Bak1986} P. Bak. The Devil's Staircase. Physics Today {\bf 39}, 12, 38 (1986).
    %reichhardt review
